### 2016-10-05 matrices.tex

When symbolic matrices are combined with the assumptions submodule for logical
inference, they provide powerful reasoning over invertibility,
semi-definiteness, orthogonality, etc., which are valuable in the construction
of numerical linear algebra systems.

>>>>

When symbolic matrices are combined with the assumptions submodule for logical
inference, they provide powerful reasoning over invertibility,
semi-definiteness, orthogonality, etc., which are valuable in the construction
of numerical linear algebra systems~\cite{rocklin2013mathematically}.

### 2016-10-05 numerics.tex

Symbolic integration and summation often produce hypergeometric
and Meijer G-function closed forms (see Subsection~\ref{sec:calculus});
numerical evaluation of such special functions is a useful complement
to direct numerical integration and summation.

>>>>

Symbolic integration and summation often produce hypergeometric
and Meijer G-function closed forms (see section~\ref{sec:calculus});
numerical evaluation of such special functions is a useful complement
to direct numerical integration and summation.

### 2016-10-05 stats.tex
Capitalization

%% Stats
The \verb|sympy.stats| submodule provides random variable types and methods for
computing of statistical properties of expressions involving random
variables, which can be either continuous or discrete, the latter ones being
further divided into finite and infinite. The variables are associated
with probability densities on corresponding domains and internally defined
in terms of probability spaces.
Apart from the possibility of defining the random variables from user supplied
density distribution, SymPy provides definitions of most common
distributions, including \texttt{Uniform}, \texttt{Poisson}, \texttt{Normal},
\texttt{Binomial}, \texttt{Bernoulli}, and many others.

@@

Using the facilities of the \texttt{sympy.stats} submodule, one can, for
example, calculate
%Using the above-mentioned features, it is easy to calculate, for example
the well known properties of maxwellian velocity distribution
\begin{verbatim}
>>> from sympy.stats import Maxwell, density
>>> kT, m, t = symbols("kT m t", positive=True)
>>> v = Maxwell("v", sqrt(kT/m))
>>> E(v)                                # mean velocity
2*sqrt(2)*sqrt(kT)/(sqrt(pi)*sqrt(m))
>>> E(v, evaluate=False)                # unevaluated mean velocity
Integral(sqrt(2)*m**(3/2)*v**3*exp(-m*v**2/(2*kT))/(sqrt(pi)*kT**(3/2)),
(v, 0, oo))
>>> E(m*v**2/2)                         # mean energy
3*kT/2
>>> solve(density(v)(t).diff(t), t)[0]  # most probable velocity
sqrt(2)*sqrt(kT)/sqrt(m)
\end{verbatim}

>>>>

%% Stats
The \verb|sympy.stats| submodule provides random variable types and methods for
computing statistical properties of expressions involving random
variables, which can be either continuous or discrete, the latter ones being
further divided into finite and infinite. The variables are associated
with probability densities on corresponding domains and internally defined
in terms of probability spaces.
Apart from the possibility of defining the random variables from a user supplied
density distribution, SymPy provides definitions of most common
distributions, including \texttt{Uniform}, \texttt{Poisson}, \texttt{Normal},
\texttt{Binomial}, \texttt{Bernoulli}, and many others.

@@

Using the facilities of the \texttt{sympy.stats} submodule, one can, for
example, calculate
%Using the above-mentioned features, it is easy to calculate, for example
the well known properties of the Maxwellian velocity distribution.
\begin{verbatim}
>>> from sympy.stats import Maxwell, density
>>> kT, m, t = symbols("kT m t", positive=True)
>>> v = Maxwell("v", sqrt(kT/m))
>>> E(v)                                # mean velocity
2*sqrt(2)*sqrt(kT)/(sqrt(pi)*sqrt(m))
>>> E(v, evaluate=False)                # unevaluated mean velocity
Integral(sqrt(2)*m**(3/2)*v**3*exp(-m*v**2/(2*kT))/(sqrt(pi)*kT**(3/2)),
(v, 0, oo))
>>> E(m*v**2/2)                         # mean energy
3*kT/2
>>> solve(density(v)(t).diff(t), t)[0]  # most probable velocity
sqrt(2)*sqrt(kT)/sqrt(m)
\end{verbatim}
